AFQ-Insight

### 2019-12-11 reports/manuscript/sections/conclusion.tex
Adds a cite to Chamberland's work.
Anticipates future work on unsupervised methods.
Add a period at the end of the last sentence.

The results we present here also motivate extensions of the method using more
sophisticated cost functions. For example, the fused sparse group lasso (FSGL)
\cite{zhou2012} extends SGL to enforce additional spatial structure: smoothness
in the variation of diffusion metrics along the tracts. As brain measurements
include additional structure (for example, bilateral symmetry), future work
could also incorporate overlapping group membership for each entry in the tract
profiles \cite{Rao2014-xm}. For example, a measurement could come from the
corpus callosum, but also from the right hemipshere. This would also require
extending the cost function used here to incorporate these constraints.

The method is packaged as open-source software called AFQ-Insight that is openly
available, and provides a clear API to allow for extensions of the method. The
sofware integrates within a broader automated fiber quantification software
ecosystem: AFQ \cite{yeatman2012tract}, which extracts tractometry data from raw
and processed dMRI datasets, as well as AFQ-Browser, which visualizes
tractometry data and facilitates sharing of the results of dMRI studies
\cite{yeatman2018browser}. To facilitate reproducibility and ease use of the
software, the results presented in this paper are also provided in
\url{https://github.com/richford/afq-insight-paper} as a series of Jupyter
notebooks
\cite{kluyver2016jupyter}

>>>>

The results we present here also motivate extensions of the method using more
sophisticated cost functions. For example, the fused sparse group lasso (FSGL)
\cite{zhou2012} extends SGL to enforce additional spatial structure: smoothness
in the variation of diffusion metrics along the tracts. As brain measurements
include additional structure (for example, bilateral symmetry), future work
could also incorporate overlapping group membership for each entry in the tract
profiles \cite{Rao2014-xm}. For example, a measurement could come from the
corpus callosum, but also from the right hemipshere. This would also require
extending the cost function used here to incorporate these constraints.
Similarly, unsupervised dimensionality reduction \cite{Chamberland2019-mu} could
also benefit from constraints based on grouping.

The method is packaged as open-source software called AFQ-Insight that is openly
available, and provides a clear API to allow for extensions of the method. The
sofware integrates within a broader automated fiber quantification software
ecosystem: AFQ \cite{yeatman2012tract}, which extracts tractometry data from raw
and processed dMRI datasets, as well as AFQ-Browser, which visualizes
tractometry data and facilitates sharing of the results of dMRI studies
\cite{yeatman2018browser}. To facilitate reproducibility and ease use of the
software, the results presented in this paper are also provided in
\url{https://github.com/richford/afq-insight-paper} as a series of Jupyter
notebooks \cite{kluyver2016jupyter}.
